### 2022-06-24 paper/main.tex
added appendix a

\documentclass[12pt,oneside, letterpaper]{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{tabu}
\usepackage{geometry}

@@

>>>>

\documentclass[12pt,oneside, letterpaper]{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{tabu}
\usepackage{geometry}
\usepackage{longtable}

@@

\begin{longtable}{| p{.6\textwidth} | p{.15\textwidth} | p{.15\textwidth} |}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \hline
    Metropolitan Statistical Area & \% Crime Posts & Diff. Score \\ \hline
    Abilene, TX Metro Area & 1.27 & -0.16 \\ \hline
    Akron, OH Metro Area & 2.34 & -0.14 \\ \hline
    Albany, GA Metro Area & 3.39 & -0.33 \\ \hline
    Albany-Lebanon, OR Metro Area & 1.67 & -0.01 \\ \hline
    Albany-Schenectady-Troy, NY Metro Area & 2.48 & -0.05 \\ \hline
    Albuquerque, NM Metro Area & 4.53 & -0.5 \\ \hline
    Alexandria, LA Metro Area & 8.82 & -0.12 \\ \hline
    Allentown-Bethlehem-Easton, PA-NJ Metro Area & 2.46 & 0.02 \\ \hline
    Altoona, PA Metro Area & 3.45 & -0.05 \\ \hline
    Amarillo, TX Metro Area & 6.6 & -0.06 \\ \hline
    Ames, IA Metro Area & 4.55 & 0.11 \\ \hline
    Anchorage, AK Metro Area & 2.36 & -0.73 \\ \hline
    Ann Arbor, MI Metro Area & 1.2 & -0.19 \\ \hline
    Anniston-Oxford, AL Metro Area & 15.69 & 0.34 \\ \hline
    Appleton, WI Metro Area & 1.53 & -0.03 \\ \hline
    Asheville, NC Metro Area & 3.35 & -0.04 \\ \hline
    Athens-Clarke County, GA Metro Area & 1.95 & -0.11 \\ \hline
    Atlanta-Sandy Springs-Alpharetta, GA Metro Area & 5.73 & 0.09 \\ \hline
    Atlantic City-Hammonton, NJ Metro Area & 1.54 & -0.1 \\ \hline
    Auburn-Opelika, AL Metro Area & 4.35 & -0.13 \\ \hline
    Augusta-Richmond County, GA-SC Metro Area & 0.93 & -0.21 \\ \hline
    Austin-Round Rock-Georgetown, TX Metro Area & 3.62 & -0.01 \\ \hline
    Bakersfield, CA Metro Area & 5.68 & -0.13 \\ \hline
    Baltimore-Columbia-Towson, MD Metro Area & 4.18 & -0.27 \\ \hline
    Bangor, ME Metro Area & 1.47 & 0.05 \\ \hline
    Barnstable Town, MA Metro Area & 1.84 & -0.13 \\ \hline
    Baton Rouge, LA Metro Area & 6.34 & -0.05 \\ \hline
    Battle Creek, MI Metro Area & 4.88 & -0.18 \\ \hline
    Bay City, MI Metro Area & 14.0 & 0.5 \\ \hline
    Beaumont-Port Arthur, TX Metro Area & 5.94 & -0.06 \\ \hline
    Beckley, WV Metro Area & 0.0 & -0.24 \\ \hline
    Bellingham, WA Metro Area & 4.06 & 0.07 \\ \hline
    Bend, OR Metro Area & 2.88 & 0.04 \\ \hline
    Billings, MT Metro Area & 1.54 & -0.3 \\ \hline
    Binghamton, NY Metro Area & 8.68 & 0.27 \\ \hline
    Birmingham-Hoover, AL Metro Area & 2.53 & -0.86 \\ \hline
    Bismarck, ND Metro Area & 0.0 & -0.22 \\ \hline
    Blacksburg-Christiansburg, VA Metro Area & 6.67 & 0.23 \\ \hline
    Bloomington, IL Metro Area & 1.63 & -0.16 \\ \hline
    Bloomington, IN Metro Area & 3.38 & -0.07 \\ \hline
    Bloomsburg-Berwick, PA Metro Area & 1.89 & -0.03 \\ \hline
    Boise City, ID Metro Area & 2.66 & -0.03 \\ \hline
    Boston-Cambridge-Newton, MA-NH Metro Area & 4.36 & 0.04 \\ \hline
    Boulder, CO Metro Area & 4.37 & 0.05 \\ \hline
    Bowling Green, KY Metro Area & 3.7 & 0.09 \\ \hline
    Bremerton-Silverdale-Port Orchard, WA Metro Area & 4.11 & 0.04 \\ \hline
    Bridgeport-Stamford-Norwalk, CT Metro Area & 1.39 & -0.05 \\ \hline
    Brownsville-Harlingen, TX Metro Area & 3.19 & -0.09 \\ \hline
    Brunswick, GA Metro Area & 7.14 & 0.13 \\ \hline
    Buffalo-Cheektowaga, NY Metro Area & 8.3 & 0.2 \\ \hline
    Burlington, NC Metro Area & 4.0 & -0.07 \\ \hline
    Burlington-South Burlington, VT Metro Area & 7.88 & 0.29 \\ \hline
    California-Lexington Park, MD Metro Area & 1.23 & -0.08 \\ \hline
    Canton-Massillon, OH Metro Area & 2.67 & -0.1 \\ \hline
    Cape Coral-Fort Myers, FL Metro Area & 5.17 & 0.1 \\ \hline
    Cape Girardeau, MO-IL Metro Area & 2.94 & -0.11 \\ \hline
    Carbondale-Marion, IL Metro Area & 1.61 & -0.5 \\ \hline
    Carson City, NV Metro Area & 1.25 & -0.18 \\ \hline
    Casper, WY Metro Area & 7.14 & 0.19 \\ \hline
    Cedar Rapids, IA Metro Area & 4.86 & 0.13 \\ \hline
    Chambersburg-Waynesboro, PA Metro Area & 0.0 & -0.12 \\ \hline
    Champaign-Urbana, IL Metro Area & 0.0 & -0.35 \\ \hline
    Charleston, WV Metro Area & 3.17 & -0.15 \\ \hline
    Charleston-North Charleston, SC Metro Area & 1.94 & -0.18 \\ \hline
    Charlotte-Concord-Gastonia, NC-SC Metro Area & 2.75 & -0.15 \\ \hline
    Charlottesville, VA Metro Area & 2.35 & 0.0 \\ \hline
    Chattanooga, TN-GA Metro Area & 3.25 & -0.2 \\ \hline
    Cheyenne, WY Metro Area & 7.36 & 0.19 \\ \hline
    Chicago-Naperville-Elgin, IL-IN-WI Metro Area & 4.86 & -0.1 \\ \hline
    Chico, CA Metro Area & 6.52 & 0.04 \\ \hline
    Cincinnati, OH-KY-IN Metro Area & 3.25 & 0.01 \\ \hline
    Clarksville, TN-KY Metro Area & 1.34 & -0.2 \\ \hline
    Cleveland, TN Metro Area & 3.33 & -0.22 \\ \hline
    Cleveland-Elyria, OH Metro Area & 2.56 & -0.15 \\ \hline
    Coeur d'Alene, ID Metro Area & 1.55 & -0.07 \\ \hline
    College Station-Bryan, TX Metro Area & 2.58 & -0.05 \\ \hline
    Colorado Springs, CO Metro Area & 2.5 & -0.2 \\ \hline
    Columbia, MO Metro Area & 0.75 & -0.15 \\ \hline
    Columbia, SC Metro Area & 4.29 & -0.18 \\ \hline
    Columbus, GA-AL Metro Area & 2.58 & -0.24 \\ \hline
    Columbus, IN Metro Area & 1.49 & -0.02 \\ \hline
    Columbus, OH Metro Area & 2.57 & -0.06 \\ \hline
    Corpus Christi, TX Metro Area & 1.44 & -0.45 \\ \hline
    Corvallis, OR Metro Area & 4.03 & 0.11 \\ \hline
    Crestview-Fort Walton Beach-Destin, FL Metro Area & 1.38 & -0.15 \\ \hline
    Cumberland, MD-WV Metro Area & 2.08 & -0.08 \\ \hline
    Dallas-Fort Worth-Arlington, TX Metro Area & 5.45 & 0.05 \\ \hline
    Dalton, GA Metro Area & 1.15 & -0.08 \\ \hline
    Danville, IL Metro Area & 0.0 & -0.67 \\ \hline
    Daphne-Fairhope-Foley, AL Metro Area & 0.0 & -0.19 \\ \hline
    Davenport-Moline-Rock Island, IA-IL Metro Area & 2.16 & -0.14 \\ \hline
    Dayton-Kettering, OH Metro Area & 1.83 & -0.13 \\ \hline
    Decatur, AL Metro Area & 10.94 & 0.38 \\ \hline
    Decatur, IL Metro Area & 0.0 & -0.3 \\ \hline
    Deltona-Daytona Beach-Ormond Beach, FL Metro Area & 2.13 & -0.11 \\ \hline
    Denver-Aurora-Lakewood, CO Metro Area & 5.67 & 0.02 \\ \hline
    Des Moines-West Des Moines, IA Metro Area & 4.06 & -0.29 \\ \hline
    Detroit-Warren-Dearborn, MI Metro Area & 3.6 & -0.17 \\ \hline
    Dothan, AL Metro Area & 0.0 & -0.43 \\ \hline
    Dover, DE Metro Area & 0.0 & -0.31 \\ \hline
    Dubuque, IA Metro Area & 1.27 & -0.03 \\ \hline
    Duluth, MN-WI Metro Area & 0.62 & -0.12 \\ \hline
    Durham-Chapel Hill, NC Metro Area & 2.23 & -0.19 \\ \hline
    East Stroudsburg, PA Metro Area & 6.25 & 0.17 \\ \hline
    Eau Claire, WI Metro Area & 4.55 & 0.1 \\ \hline
    El Centro, CA Metro Area & 1.92 & -0.14 \\ \hline
    El Paso, TX Metro Area & 3.09 & -0.07 \\ \hline
    Elizabethtown-Fort Knox, KY Metro Area & 1.92 & 0.03 \\ \hline
    Elkhart-Goshen, IN Metro Area & 4.92 & -0.29 \\ \hline
    Elmira, NY Metro Area & 1.96 & -0.05 \\ \hline
    Enid, OK Metro Area & 5.26 & 0.02 \\ \hline
    Erie, PA Metro Area & 3.36 & -0.03 \\ \hline
    Eugene-Springfield, OR Metro Area & 3.97 & 0.05 \\ \hline
    Evansville, IN-KY Metro Area & 1.12 & -0.17 \\ \hline
    Fairbanks, AK Metro Area & 1.42 & -0.49 \\ \hline
    Fargo, ND-MN Metro Area & 2.77 & -0.06 \\ \hline
    Farmington, NM Metro Area & 1.61 & -0.77 \\ \hline
    Fayetteville, NC Metro Area & 4.07 & -0.4 \\ \hline
    Fayetteville-Springdale-Rogers, AR Metro Area & 2.44 & -0.14 \\ \hline
    Flagstaff, AZ Metro Area & 1.07 & -0.27 \\ \hline
    Flint, MI Metro Area & 9.71 & 0.12 \\ \hline
    Florence, SC Metro Area & 3.51 & -0.4 \\ \hline
    Florence-Muscle Shoals, AL Metro Area & 6.45 & 0.14 \\ \hline
    Fond du Lac, WI Metro Area & 0.0 & -0.13 \\ \hline
    Fort Collins, CO Metro Area & 3.0 & -0.0 \\ \hline
    Fort Smith, AR-OK Metro Area & 1.52 & -0.34 \\ \hline
    Fort Wayne, IN Metro Area & 2.44 & -0.08 \\ \hline
    Fresno, CA Metro Area & 1.88 & -0.32 \\ \hline
    Gadsden, AL Metro Area & 2.04 & -0.27 \\ \hline
    Gainesville, FL Metro Area & 2.57 & -0.35 \\ \hline
    Gainesville, GA Metro Area & 1.61 & -0.06 \\ \hline
    Gettysburg, PA Metro Area & 2.86 & 0.06 \\ \hline
    Glens Falls, NY Metro Area & 5.08 & 0.19 \\ \hline
    Goldsboro, NC Metro Area & 0.0 & -0.3 \\ \hline
    Grand Forks, ND-MN Metro Area & 1.32 & -0.11 \\ \hline
    Grand Island, NE Metro Area & 0.0 & -0.27 \\ \hline
    Grand Junction, CO Metro Area & 4.32 & 0.03 \\ \hline
    Grand Rapids-Kentwood, MI Metro Area & 5.08 & 0.05 \\ \hline
    Grants Pass, OR Metro Area & 7.25 & 0.23 \\ \hline
    Great Falls, MT Metro Area & 7.69 & 0.17 \\ \hline
    Greeley, CO Metro Area & 6.38 & 0.2 \\ \hline
    Green Bay, WI Metro Area & 3.62 & 0.04 \\ \hline
    Greensboro-High Point, NC Metro Area & 2.38 & -0.25 \\ \hline
    Greenville, NC Metro Area & 2.06 & -0.15 \\ \hline
    Greenville-Anderson, SC Metro Area & 1.36 & -0.27 \\ \hline
    Gulfport-Biloxi, MS Metro Area & 1.15 & -0.1 \\ \hline
    Hagerstown-Martinsburg, MD-WV Metro Area & 3.41 & -0.01 \\ \hline
    Hammond, LA Metro Area & 5.56 & -0.3 \\ \hline
    Hanford-Corcoran, CA Metro Area & 4.0 & -0.14 \\ \hline
    Harrisburg-Carlisle, PA Metro Area & 1.38 & -0.11 \\ \hline
    Harrisonburg, VA Metro Area & 3.72 & 0.11 \\ \hline
    Hartford-East Hartford-Middletown, CT Metro Area & 2.27 & -0.02 \\ \hline
    Hattiesburg, MS Metro Area & 0.0 & -0.17 \\ \hline
    Hickory-Lenoir-Morganton, NC Metro Area & 3.57 & -0.11 \\ \hline
    Hilton Head Island-Bluffton, SC Metro Area & 0.0 & -0.28 \\ \hline
    Hinesville, GA Metro Area & 0.0 & -0.3 \\ \hline
    Homosassa Springs, FL Metro Area & 0.0 & -0.18 \\ \hline
    Hot Springs, AR Metro Area & 1.98 & -0.27 \\ \hline
    Houma-Thibodaux, LA Metro Area & 3.51 & -0.07 \\ \hline
    Houston-The Woodlands-Sugar Land, TX Metro Area & 5.02 & -0.15 \\ \hline
    Huntington-Ashland, WV-KY-OH Metro Area & 4.11 & 0.04 \\ \hline
    Huntsville, AL Metro Area & 1.94 & -0.29 \\ \hline
    Idaho Falls, ID Metro Area & 4.26 & 0.09 \\ \hline
    Indianapolis-Carmel-Anderson, IN Metro Area & 4.19 & -0.23 \\ \hline
    Iowa City, IA Metro Area & 2.98 & -0.03 \\ \hline
    Ithaca, NY Metro Area & 2.68 & 0.06 \\ \hline
    Jackson, MI Metro Area & 4.0 & -0.15 \\ \hline
    Jackson, MS Metro Area & 3.37 & -0.06 \\ \hline
    Jackson, TN Metro Area & 0.0 & -0.44 \\ \hline
    Jacksonville, FL Metro Area & 2.48 & -0.2 \\ \hline
    Jacksonville, NC Metro Area & 1.85 & -0.09 \\ \hline
    Janesville-Beloit, WI Metro Area & 5.17 & 0.12 \\ \hline
    Jefferson City, MO Metro Area & 0.0 & -0.16 \\ \hline
    Johnson City, TN Metro Area & 2.13 & -0.12 \\ \hline
    Johnstown, PA Metro Area & 7.14 & 0.2 \\ \hline
    Jonesboro, AR Metro Area & 2.0 & -0.29 \\ \hline
    Joplin, MO Metro Area & 4.17 & -0.01 \\ \hline
    Kahului-Wailuku-Lahaina, HI Metro Area & 0.98 & -0.14 \\ \hline
    Kalamazoo-Portage, MI Metro Area & 2.55 & -0.27 \\ \hline
    Kankakee, IL Metro Area & 1.89 & -0.17 \\ \hline
    Kansas City, MO-KS Metro Area & 3.16 & -0.66 \\ \hline
    Kennewick-Richland, WA Metro Area & 3.94 & 0.06 \\ \hline
    Killeen-Temple, TX Metro Area & 5.68 & 0.12 \\ \hline
    Kingsport-Bristol, TN-VA Metro Area & 6.15 & 0.12 \\ \hline
    Kingston, NY Metro Area & 1.92 & -0.0 \\ \hline
    Knoxville, TN Metro Area & 2.78 & -0.1 \\ \hline
    Kokomo, IN Metro Area & 6.45 & -0.04 \\ \hline
    La Crosse-Onalaska, WI-MN Metro Area & 4.9 & 0.18 \\ \hline
    Lafayette, LA Metro Area & 6.12 & 0.0 \\ \hline
    Lafayette-West Lafayette, IN Metro Area & 2.75 & -0.01 \\ \hline
    Lake Charles, LA Metro Area & 2.08 & -0.28 \\ \hline
    Lake Havasu City-Kingman, AZ Metro Area & 1.96 & -0.06 \\ \hline
    Lakeland-Winter Haven, FL Metro Area & 2.94 & -0.04 \\ \hline
    Lancaster, PA Metro Area & 1.96 & -0.02 \\ \hline
    Lansing-East Lansing, MI Metro Area & 4.79 & -0.04 \\ \hline
    Laredo, TX Metro Area & 0.0 & -0.23 \\ \hline
    Las Cruces, NM Metro Area & 5.53 & -0.09 \\ \hline
    Las Vegas-Henderson-Paradise, NV Metro Area & 2.32 & -0.25 \\ \hline
    Lawrence, KS Metro Area & 3.67 & -0.08 \\ \hline
    Lawton, OK Metro Area & 1.82 & -0.41 \\ \hline
    Lebanon, PA Metro Area & 0.0 & -0.12 \\ \hline
    Lewiston, ID-WA Metro Area & 12.96 & 0.61 \\ \hline
    Lewiston-Auburn, ME Metro Area & 15.38 & 0.72 \\ \hline
    Lexington-Fayette, KY Metro Area & 2.02 & -0.05 \\ \hline
    Lima, OH Metro Area & 4.0 & -0.01 \\ \hline
    Lincoln, NE Metro Area & 3.05 & -0.08 \\ \hline
    Little Rock-North Little Rock-Conway, AR Metro Area & 7.08 & -0.17 \\ \hline
    Logan, UT-ID Metro Area & 3.42 & 0.1 \\ \hline
    Longview, TX Metro Area & 1.49 & -0.15 \\ \hline
    Longview, WA Metro Area & 5.36 & 0.16 \\ \hline
    Los Angeles-Long Beach-Anaheim, CA Metro Area & 12.0 & 0.32 \\ \hline
    Louisville/Jefferson County, KY-IN Metro Area & 4.4 & -0.07 \\ \hline
    Lubbock, TX Metro Area & 2.02 & -0.49 \\ \hline
    Lynchburg, VA Metro Area & 2.7 & -0.02 \\ \hline
    Macon-Bibb County, GA Metro Area & 2.88 & -0.17 \\ \hline
    Madera, CA Metro Area & 0.0 & -0.38 \\ \hline
    Madison, WI Metro Area & 3.79 & 0.05 \\ \hline
    Manchester-Nashua, NH Metro Area & 1.23 & -0.1 \\ \hline
    Manhattan, KS Metro Area & 4.05 & -0.09 \\ \hline
    Mankato, MN Metro Area & 0.0 & -0.13 \\ \hline
    Mansfield, OH Metro Area & 0.0 & -0.16 \\ \hline
    McAllen-Edinburg-Mission, TX Metro Area & 3.26 & -0.01 \\ \hline
    Medford, OR Metro Area & 6.74 & 0.13 \\ \hline
    Memphis, TN-MS-AR Metro Area & 3.43 & -0.61 \\ \hline
    Merced, CA Metro Area & 4.29 & -0.16 \\ \hline
    Miami-Fort Lauderdale-Pompano Beach, FL Metro Area & 3.28 & -0.12 \\ \hline
    Michigan City-La Porte, IN Metro Area & 1.1 & -0.23 \\ \hline
    Midland, MI Metro Area & 3.08 & 0.07 \\ \hline
    Midland, TX Metro Area & 4.3 & 0.01 \\ \hline
    Milwaukee-Waukesha, WI Metro Area & 4.09 & -0.19 \\ \hline
    Minneapolis-St. Paul-Bloomington, MN-WI Metro Area & 5.87 & 0.13 \\ \hline
    Missoula, MT Metro Area & 2.45 & -0.12 \\ \hline
    Mobile, AL Metro Area & 2.79 & -0.22 \\ \hline
    Modesto, CA Metro Area & 2.76 & -0.23 \\ \hline
    Monroe, LA Metro Area & 0.0 & -0.58 \\ \hline
    Monroe, MI Metro Area & 3.28 & -0.01 \\ \hline
    Montgomery, AL Metro Area & 2.36 & -0.2 \\ \hline
    Morgantown, WV Metro Area & 0.95 & -0.09 \\ \hline
    Morristown, TN Metro Area & 9.3 & 0.23 \\ \hline
    Mount Vernon-Anacortes, WA Metro Area & 3.66 & 0.09 \\ \hline
    Muncie, IN Metro Area & 7.94 & 0.26 \\ \hline
    Muskegon, MI Metro Area & 7.21 & 0.07 \\ \hline
    Myrtle Beach-Conway-North Myrtle Beach, SC-NC Metro Area & 1.74 & -0.16 \\ \hline
    Napa, CA Metro Area & 4.72 & -0.13 \\ \hline
    Naples-Marco Island, FL Metro Area & 3.72 & 0.04 \\ \hline
    Nashville-Davidson--Murfreesboro--Franklin, TN Metro Area & 3.76 & -0.2 \\ \hline
    New Bern, NC Metro Area & 0.0 & -0.2 \\ \hline
    New Haven-Milford, CT Metro Area & 2.57 & -0.05 \\ \hline
    New Orleans-Metairie, LA Metro Area & 5.29 & -0.1 \\ \hline
    New York-Newark-Jersey City, NY-NJ-PA Metro Area & 10.72 & 0.35 \\ \hline
    Niles, MI Metro Area & 4.08 & -0.17 \\ \hline
    North Port-Sarasota-Bradenton, FL Metro Area & 2.38 & -0.1 \\ \hline
    Norwich-New London, CT Metro Area & 6.48 & 0.22 \\ \hline
    Ocala, FL Metro Area & 2.42 & -0.18 \\ \hline
    Ocean City, NJ Metro Area & 1.67 & -0.03 \\ \hline
    Odessa, TX Metro Area & 4.3 & -0.39 \\ \hline
    Ogden-Clearfield, UT Metro Area & 1.75 & -0.03 \\ \hline
    Oklahoma City, OK Metro Area & 3.17 & -0.16 \\ \hline
    Olympia-Lacey-Tumwater, WA Metro Area & 3.54 & 0.02 \\ \hline
    Omaha-Council Bluffs, NE-IA Metro Area & 2.91 & -0.14 \\ \hline
    Orlando-Kissimmee-Sanford, FL Metro Area & 2.61 & -0.16 \\ \hline
    Oshkosh-Neenah, WI Metro Area & 1.75 & -0.04 \\ \hline
    Owensboro, KY Metro Area & 3.17 & 0.08 \\ \hline
    Oxnard-Thousand Oaks-Ventura, CA Metro Area & 2.31 & -0.03 \\ \hline
    Palm Bay-Melbourne-Titusville, FL Metro Area & 2.79 & -0.11 \\ \hline
    Panama City, FL Metro Area & 2.78 & -0.16 \\ \hline
    Parkersburg-Vienna, WV Metro Area & 0.0 & -0.31 \\ \hline
    Pensacola-Ferry Pass-Brent, FL Metro Area & 2.07 & -0.18 \\ \hline
    Peoria, IL Metro Area & 0.96 & -0.27 \\ \hline
    Philadelphia-Camden-Wilmington, PA-NJ-DE-MD Metro Area & 6.69 & 0.08 \\ \hline
    Phoenix-Mesa-Chandler, AZ Metro Area & 3.49 & -0.11 \\ \hline
    Pine Bluff, AR Metro Area & 12.5 & 0.05 \\ \hline
    Pittsburgh, PA Metro Area & 3.76 & 0.01 \\ \hline
    Pittsfield, MA Metro Area & 2.0 & -0.16 \\ \hline
    Pocatello, ID Metro Area & 2.53 & -0.07 \\ \hline
    Port St. Lucie, FL Metro Area & 5.48 & 0.13 \\ \hline
    Portland-South Portland, ME Metro Area & 3.07 & 0.09 \\ \hline
    Portland-Vancouver-Hillsboro, OR-WA Metro Area & 11.36 & 0.41 \\ \hline
    Poughkeepsie-Newburgh-Middletown, NY Metro Area & 1.92 & -0.03 \\ \hline
    Prescott Valley-Prescott, AZ Metro Area & 0.0 & -0.2 \\ \hline
    Providence-Warwick, RI-MA Metro Area & 2.82 & -0.05 \\ \hline
    Provo-Orem, UT Metro Area & 0.0 & -0.06 \\ \hline
    Pueblo, CO Metro Area & 2.26 & -0.37 \\ \hline
    Punta Gorda, FL Metro Area & 0.0 & -0.14 \\ \hline
    Racine, WI Metro Area & 5.63 & 0.08 \\ \hline
    Raleigh-Cary, NC Metro Area & 1.9 & -0.02 \\ \hline
    Rapid City, SD Metro Area & 6.78 & -0.01 \\ \hline
    Reading, PA Metro Area & 0.0 & -0.17 \\ \hline
    Redding, CA Metro Area & 8.33 & -0.01 \\ \hline
    Reno, NV Metro Area & 2.27 & -0.21 \\ \hline
    Richmond, VA Metro Area & 2.68 & -0.02 \\ \hline
    Riverside-San Bernardino-Ontario, CA Metro Area & 6.62 & 0.06 \\ \hline
    Roanoke, VA Metro Area & 0.32 & -0.15 \\ \hline
    Rochester, MN Metro Area & 1.79 & -0.01 \\ \hline
    Rochester, NY Metro Area & 3.5 & 0.01 \\ \hline
    Rockford, IL Metro Area & 8.06 & -0.01 \\ \hline
    Rocky Mount, NC Metro Area & 11.29 & 0.32 \\ \hline
    Rome, GA Metro Area & 0.0 & -0.24 \\ \hline
    Sacramento-Roseville-Folsom, CA Metro Area & 6.15 & 0.08 \\ \hline
    Saginaw, MI Metro Area & 4.88 & -0.18 \\ \hline
    Salem, OR Metro Area & 5.94 & 0.13 \\ \hline
    Salinas, CA Metro Area & 5.71 & 0.08 \\ \hline
    Salisbury, MD-DE Metro Area & 1.72 & -0.14 \\ \hline
    Salt Lake City, UT Metro Area & 2.44 & -0.13 \\ \hline
    San Angelo, TX Metro Area & 0.0 & -0.23 \\ \hline
    San Antonio-New Braunfels, TX Metro Area & 3.83 & -0.16 \\ \hline
    San Diego-Chula Vista-Carlsbad, CA Metro Area & 4.26 & -0.01 \\ \hline
    San Francisco-Oakland-Berkeley, CA Metro Area & 7.31 & 0.07 \\ \hline
    San Jose-Sunnyvale-Santa Clara, CA Metro Area & 4.73 & 0.03 \\ \hline
    San Luis Obispo-Paso Robles, CA Metro Area & 5.51 & 0.14 \\ \hline
    Santa Cruz-Watsonville, CA Metro Area & 3.07 & -0.12 \\ \hline
    Santa Fe, NM Metro Area & 1.16 & -0.22 \\ \hline
    Santa Maria-Santa Barbara, CA Metro Area & 1.85 & -0.14 \\ \hline
    Santa Rosa-Petaluma, CA Metro Area & 3.03 & -0.12 \\ \hline
    Savannah, GA Metro Area & 2.4 & -0.14 \\ \hline
    Scranton--Wilkes-Barre, PA Metro Area & 1.59 & -0.2 \\ \hline
    Seattle-Tacoma-Bellevue, WA Metro Area & 18.17 & 0.74 \\ \hline
    Sebastian-Vero Beach, FL Metro Area & 1.89 & -0.05 \\ \hline
    Sebring-Avon Park, FL Metro Area & 0.0 & -0.19 \\ \hline
    Sheboygan, WI Metro Area & 6.67 & 0.24 \\ \hline
    Sherman-Denison, TX Metro Area & 0.0 & -0.18 \\ \hline
    Shreveport-Bossier City, LA Metro Area & 4.39 & -0.16 \\ \hline
    Sierra Vista-Douglas, AZ Metro Area & 5.63 & 0.15 \\ \hline
    Sioux City, IA-NE-SD Metro Area & 6.1 & 0.11 \\ \hline
    Sioux Falls, SD Metro Area & 1.23 & -0.21 \\ \hline
    South Bend-Mishawaka, IN-MI Metro Area & 2.48 & -0.18 \\ \hline
    Spartanburg, SC Metro Area & 1.12 & -0.3 \\ \hline
    Spokane-Spokane Valley, WA Metro Area & 4.67 & -0.02 \\ \hline
    Springfield, IL Metro Area & 2.73 & -0.27 \\ \hline
    Springfield, MA Metro Area & 6.03 & -0.01 \\ \hline
    Springfield, MO Metro Area & 3.79 & -0.24 \\ \hline
    Springfield, OH Metro Area & 0.0 & -0.18 \\ \hline
    St. Cloud, MN Metro Area & 8.0 & 0.31 \\ \hline
    St. George, UT Metro Area & 2.02 & -0.01 \\ \hline
    St. Joseph, MO-KS Metro Area & 6.0 & 0.04 \\ \hline
    St. Louis, MO-IL Metro Area & 3.91 & -0.11 \\ \hline
    State College, PA Metro Area & 4.94 & 0.18 \\ \hline
    Staunton, VA Metro Area & 1.39 & -0.05 \\ \hline
    Stockton, CA Metro Area & 6.14 & -0.23 \\ \hline
    Sumter, SC Metro Area & 9.26 & -0.0 \\ \hline
    Syracuse, NY Metro Area & 4.15 & 0.03 \\ \hline
    Tallahassee, FL Metro Area & 1.49 & -0.3 \\ \hline
    Tampa-St. Petersburg-Clearwater, FL Metro Area & 4.15 & 0.02 \\ \hline
    Terre Haute, IN Metro Area & 1.01 & -0.14 \\ \hline
    Texarkana, TX-AR Metro Area & 6.67 & 0.04 \\ \hline
    The Villages, FL Metro Area & 2.04 & -0.02 \\ \hline
    Toledo, OH Metro Area & 2.98 & -0.17 \\ \hline
    Topeka, KS Metro Area & 3.41 & -0.17 \\ \hline
    Trenton-Princeton, NJ Metro Area & 5.36 & 0.05 \\ \hline
    Tucson, AZ Metro Area & 1.94 & -0.21 \\ \hline
    Tulsa, OK Metro Area & 4.04 & -0.16 \\ \hline
    Tuscaloosa, AL Metro Area & 5.52 & 0.02 \\ \hline
    Twin Falls, ID Metro Area & 3.45 & -0.02 \\ \hline
    Tyler, TX Metro Area & 1.99 & -0.13 \\ \hline
    Urban Honolulu, HI Metro Area & 5.91 & 0.13 \\ \hline
    Utica-Rome, NY Metro Area & 1.06 & -0.14 \\ \hline
    Valdosta, GA Metro Area & 6.76 & 0.15 \\ \hline
    Vallejo, CA Metro Area & 8.82 & 0.15 \\ \hline
    Victoria, TX Metro Area & 2.0 & -0.22 \\ \hline
    Vineland-Bridgeton, NJ Metro Area & 4.35 & -0.06 \\ \hline
    Virginia Beach-Norfolk-Newport News, VA-NC Metro Area & 5.67 & 0.06 \\ \hline
    Visalia, CA Metro Area & 4.27 & -0.03 \\ \hline
    Waco, TX Metro Area & 7.92 & 0.13 \\ \hline
    Walla Walla, WA Metro Area & 2.47 & -0.03 \\ \hline
    Warner Robins, GA Metro Area & 5.08 & -0.02 \\ \hline
    Washington-Arlington-Alexandria, DC-VA-MD-WV Metro Area & 4.92 & 0.08 \\ \hline
    Waterloo-Cedar Falls, IA Metro Area & 1.43 & -0.15 \\ \hline
    Watertown-Fort Drum, NY Metro Area & 4.55 & 0.09 \\ \hline
    Wausau-Weston, WI Metro Area & 4.11 & 0.07 \\ \hline
    Weirton-Steubenville, WV-OH Metro Area & 5.45 & 0.19 \\ \hline
    Wenatchee, WA Metro Area & 5.22 & 0.21 \\ \hline
    Wheeling, WV-OH Metro Area & 1.61 & -0.13 \\ \hline
    Wichita Falls, TX Metro Area & 3.85 & -0.03 \\ \hline
    Wichita, KS Metro Area & 2.85 & -0.4 \\ \hline
    Williamsport, PA Metro Area & 2.99 & 0.04 \\ \hline
    Wilmington, NC Metro Area & 3.63 & -0.07 \\ \hline
    Winchester, VA-WV Metro Area & 0.0 & -0.12 \\ \hline
    Winston-Salem, NC Metro Area & 2.32 & -0.64 \\ \hline
    Worcester, MA-CT Metro Area & 2.58 & -0.08 \\ \hline
    Yakima, WA Metro Area & 5.38 & 0.1 \\ \hline
    York-Hanover, PA Metro Area & 1.41 & -0.1 \\ \hline
    Youngstown-Warren-Boardman, OH-PA Metro Area & 1.8 & -0.37 \\ \hline
    Yuba City, CA Metro Area & 5.17 & 0.02 \\ \hline
    Yuma, AZ Metro Area & 0.86 & -0.15 \\ \hline
    \caption{Metropolitan Areas and their subreddits}
	\label{table:app-a}
\end{longtable}
